\startproduct product-quicksilver-book
\project project-quicksilver

\startfrontmatter
  \noheaderandfooterlines

  % Title page
  \dontleavehmode
  \blank[4cm]
  \startalignment[center]
    \ssd Quicksilver \par
    \ssc From Munich to Lake Como
  \stopalignment
  \blank[6cm]
  \startalignment[flushright]
    \dontleavehmode
    \ssb
    \bTABLE
    \setupTABLE[r][each][frame=off]
    \bTR \bTD Michael V. Stanton \eTD \eTR
    \eTABLE
  \stopalignment
  \page

  % copyright
  \noheaderandfooterlines
  \dontleavehmode
  \blank[9cm]
  \noindenting
  All rights reserved. No part of this publication may be reproduced,
  stored in a retrieval system, or transmitted in any form or by any
  means, electronic, mechanical, photocopying, recording or otherwise,
  without prior written permission of the publisher. \par
 
  Copyright 2015 Michael V. Stanton, Bruderstrasse 8, 80538
  Munich, Germany. Published with Lulu.com.\par

  Email: \type{ripsawridge@gmail.com}
  \par

  Web: \type{http://www.mountainwerks.org/}
  \par
  \page 

  % Table of contents
  \completecontent

  % Introduction
  \chapter{Introduction}
  
  By the year 2000, I was practically dreaming about the deep forests
  and glaciers of the Cascades every night. After one of the wettest
  winters on record, I discovered the benefits of travelling east to
  find sun. Leavenworth became one of my favorite places to
  climb. Steve Nesland joined me on most trips, including the
  memorable climb of Prusik Peak with Jack and Peter as well. Our trip
  to the Tetons was the centerpiece of the summer, and provided hours
  of dreamlike climbing in the warm Wyoming sun. 

  Kris joined me for some great rock climbing trips, which gave us the
  confidence to plan our Italian Dolomites trip for 2001. 

  \startalignment[flushright]
  {\em Michael Stanton} \par
  {\em Munich, 2015}
  \stopalignment

\stopfrontmatter

\startbodymatter

  \component introduction/introduction.tex
  \component stage0/stage0.tex
  \component stage1/stage1.tex
  \component stage2/stage2.tex
  \component stage3/stage3.tex
  \component stage4/stage4.tex
  \component stage5/stage5.tex
  \component afterward/afterward.tex

\stopbodymatter

\startbackmatter

  % Index
  \completeindex

  % about the author
  \title{About the Author}
  
  Michael Stanton is a software engineer living in Munich, Germany.
  He discovered rock and mountain climbing in the Cascades of Washington
  State, and has been obsessed ever since. 

  \title{Colophon}

  This book was created with \TEX\ and \CONTEXT\ on a MacBook.
  Emacs was used to edit the files. The typeface is Palantino 11 point.

\stopbackmatter

\stopproduct

